Visualization of [fulle name] Fractional Integrals

### 2019-05-27 fractional/CMJ style files/article-template.tex
added file to x

\noindent
In this article we specifically focus on the geometric interpretation of fractional integrals. To be more specific, we present a novel geometric interpretation of the Riemann-Liouville fractional integral \cite{laurent1884}.
As we mentioned earlier, Riemann and Liouville played an important role in the development of fractional calculus. Their work was crucial in defining what is now know as 
the Riemann-Liouville fractional integral \cite{laurent1884}. At this point in time the reader should be made aware of the fact that there exists many other accepted fractional integral definitions in the literature.
We, however, do not discuss them any further in this article. Investigating whether one can apply the proposed framework to other fractional integral definitions will be presented in future work. The geometric interpretation we present in this paper is an extension of the fractional geometric framework presented by Podlubny \cite{podlubny02}. Podlubny showed that a fractional Riemann-Liouville 
integral can be converted to a Riemann-Stieltjes integral. Furthermore, Grobler showed that a Riemann-Stieltjes integral can be interpreted as an infiniesimal sum of 
non-rectangular infinitesimels, i.e. a Riemann-Stieltjes integral can be converted into a Cavalieri integral \cite{ackermann12,?}. Combining these two ideas together results in the following geometric 
interpretation: the Riemann-Liouville fractional integral can be interpreted as an infinite sum of non-rectangular infinitesimals whose shape is determined by the order of integration $\alpha$ and the integration limit $t$.\\

>>>>

\noindent
In this article we specifically focus on the geometric interpretation of fractional integrals. To be more specific, we present a novel geometric interpretation of the Riemann-Liouville fractional integral \cite{laurent1884}.
As we mentioned earlier, Riemann and Liouville played an important role in the development of fractional calculus. Their work was crucial in defining what is now know as 
the Riemann-Liouville fractional integral \cite{laurent1884}. At this point in time the reader should be made aware of the fact that there exists many other accepted fractional integral definitions in the literature.
We, however, deem thhese definitions to be beyond the scope of the current article and as such we do not discuss them any further in this work. The geometric interpretation 
we present here is an extension of the geometric interpretation presented by Podlubny\cite{podlubny02}. Podlubny showed that a Riemann-Liouville fractional integral 
can be converted into a Riemann-Stieltjes integral. Furthermore, Grobler showed that a Riemann-Stieltjes integral can be interpreted as the are obtained by summing toghether 
the area of an infinite number of non-rectangular infinitesimels, i.e. a Riemann-Stieltjes integral can be converted into a Cavalieri integral \cite{ackermann12,?}. Combining these two ideas together results in the following geometric 
interpretation: the Riemann-Liouville fractional integral can be interpreted as an infinite sum of non-rectangular infinitesimals whose shape is determined by the order of integration $\alpha$ and the integration limit $t$.\\
